% APA-style bibliography 
\begin{thebibliography}{30}

\bibitem{lit1} E. Wyss, ``A new frontier for software security: Diving deep into npm,'' 2025.

\bibitem{lit7} M. Wang, P. Wu, and Q. Luo, ``Construction of software supply chain threat portrait based on chain perspective,'' 2023.

\bibitem{lit8} C. Liu et al., ``Demystifying vulnerability propagation via dependency trees in npm,'' in \textit{ICSE}, 2022.

\bibitem{lit18} A. Zerouali et al., ``On the impact of security vulnerabilities in the npm and RubyGems dependency networks,'' 2022.

\bibitem{lit5} I. Rahman et al., ``Characterizing dependency update practice of NPM, PyPI and Cargo packages,'' 2024.

\bibitem{lit22} F. R. Cogo, ``Studying dependency maintenance practices through mining NPM,'' 2020.

\bibitem{lit10} A. J. Jafari et al., ``Dependency practices for vulnerability mitigation,'' 2023.

\bibitem{lit20} M. Zimmermann et al., ``Small world with high risks: Security threats in npm,'' in \textit{USENIX Sec.}, 2019.

\bibitem{lit16} A. Hafner, A. Mur, and J. Bernard, ``Node package manager's dependency network robustness,'' 2021.

\bibitem{lit25} E.-R. Oldnall, ``The web of dependencies: A complex network analysis of the NPM,'' 2017.

\bibitem{lit2} P. Jaisri, B. Reid, and R. G. Kula, ``A preliminary study on self-contained libraries in the NPM ecosystem,'' 2024.

\bibitem{lit6} T. G. Hastings, ``Combating source poisoning and next-generation software supply chain attacks,'' 2024.

\bibitem{lit30} M. Shcherbakov, P. Moosbrugger, and M. Balliu, ``Unveiling the invisible: Prototype pollution gadgets via dynamic taint,'' 2021.

\bibitem{lit12} D. Y. K. Yip, ``Empirical study on dependency-based attacks in Node.js,'' 2022.

\bibitem{lit4} M. Ohm et al., ``Backstabber's knife collection: A review of open source software supply chain attacks,'' in \textit{DIMVA}, 2020.

\bibitem{lit24} P. Ladisa et al., ``The hitchhiker's guide to malicious third-party dependencies,'' in \textit{IEEE S\&P}, 2023.

\bibitem{lit28} R. Duan et al., ``Towards measuring supply chain attacks on package managers,'' in \textit{NDSS}, 2020.

\bibitem{lit19} A. Sejfia and M. Schafer, ``Practical automated detection of malicious npm packages (Amalfi),'' in \textit{ICSE}, 2022.

\bibitem{lit29} X. Zheng et al., ``Towards robust detection of OSS supply chain poisoning (OSCAR),'' 2024.

\bibitem{lit15} S. Halder et al., ``Malicious package detection using metadata information,'' 2024.

\bibitem{lit14} J. Zhang et al., ``Malicious package detection in NPM and PyPI using a single model of malicious behavior sequence,'' 2023.

\bibitem{lit17} P. Ladisa et al., ``On the feasibility of cross-language detection of malicious packages in npm and PyPI,'' 2023.

\bibitem{lit11} M. L. P. Correia, ``Detection of software supply chain attacks in code repositories,'' 2022.

\bibitem{lit23} M. Ohm et al., ``Supporting detection via unsupervised signature generation (ACME),'' 2021.

\bibitem{lit13} S. Torres-Arias, ``In-toto: Practical software supply chain security,'' in \textit{USENIX Sec.}, 2020.

\bibitem{lit3} S. Yu, ``Accurate and efficient SBOM generation for software supply chain security,'' 2024.

\bibitem{lit9} H. E. Ahlstrom, ``Dependency analysis for software licensing and security,'' 2025.

\bibitem{lit21} T. R. Schorlemmer, ``Software supply chain security: Attacks, defenses, and signing adoption,'' 2024.

\bibitem{lit26} N. Imtiaz, ``Toward secure use of open source dependencies,'' 2023.

\bibitem{lit27} S. Vaidya, ``Towards ensuring integrity and authenticity of software repositories,'' 2022.

\end{thebibliography}
