% APA-style bibliography 
\begin{thebibliography}{30}

\bibitem{wyss2025npm} E. Wyss, ``A new frontier for software security: Diving deep into npm,'' 2025.
\bibitem{duan2020measuring} R. Duan et al., ``Towards measuring supply chain attacks on package managers,'' in \textit{NDSS}, 2020.
\bibitem{wang2023threat} M. Wang, P. Wu, and Q. Luo, ``Construction of software supply chain threat portrait based on chain perspective,'' 2023.
\bibitem{liu2022demystifying} C. Liu et al., ``Demystifying vulnerability propagation via dependency trees in npm,'' in \textit{ICSE}, 2022.
\bibitem{zerouali2022impact} A. Zerouali et al., ``On the impact of security vulnerabilities in the npm and RubyGems dependency networks,'' 2022.
\bibitem{rahman2024update} I. Rahman et al., ``Characterizing dependency update practice of NPM, PyPI and Cargo packages,'' 2024.
\bibitem{cogo2020maintenance} F. R. Cogo, ``Studying dependency maintenance practices through mining NPM,'' 2020.
\bibitem{jafari2023mitigation} A. J. Jafari et al., ``Dependency practices for vulnerability mitigation,'' 2023.
\bibitem{zimmermann2019smallworld} M. Zimmermann et al., ``Small world with high risks: Security threats in npm,'' in \textit{USENIX Sec.}, 2019.
\bibitem{hafner2021robustness} A. Hafner, A. Mur, and J. Bernard, ``Node package manager's dependency network robustness,'' 2021.
\bibitem{oldnall2017complex} E.-R. Oldnall, ``The web of dependencies: A complex network analysis of the NPM,'' 2017.
\bibitem{jaisri2024selfcontained} P. Jaisri, B. Reid, and R. G. Kula, ``A preliminary study on self-contained libraries in the NPM ecosystem,'' 2024.
\bibitem{ohm2020backstabber} M. Ohm et al., ``Backstabber's knife collection: A review of open source software supply chain attacks,'' in \textit{DIMVA}, 2020.
\bibitem{hastings2024poisoning} T. G. Hastings, ``Combating source poisoning and next-generation software supply chain attacks,'' 2024.
\bibitem{shcherbakov2021prototype} M. Shcherbakov, P. Moosbrugger, and M. Balliu, ``Unveiling the invisible: Prototype pollution gadgets via dynamic taint,'' 2021.
\bibitem{yip2022dependency} D. Y. K. Yip, ``Empirical study on dependency-based attacks in Node.js,'' 2022.
\bibitem{ladisa2023hitchhiker} P. Ladisa et al., ``The hitchhiker's guide to malicious third-party dependencies,'' in \textit{IEEE S\&P}, 2023.
\bibitem{sejfia2022amalfi} A. Sejfia and M. Schafer, ``Practical automated detection of malicious npm packages (Amalfi),'' in \textit{ICSE}, 2022.
\bibitem{zheng2024oscar} X. Zheng et al., ``Towards robust detection of OSS supply chain poisoning (OSCAR),'' 2024.
\bibitem{halder2024metadata} S. Halder et al., ``Malicious package detection using metadata information,'' 2024.
\bibitem{zhang2023behavior} J. Zhang et al., ``Malicious package detection in NPM and PyPI using a single model of malicious behavior sequence,'' 2023.
\bibitem{ladisa2023crosslang} P. Ladisa et al., ``On the feasibility of cross-language detection of malicious packages in npm and PyPI,'' 2023.
\bibitem{imtiaz2023secure} N. Imtiaz, ``Toward secure use of open source dependencies,'' 2023.
\bibitem{correia2022detection} M. L. P. Correia, ``Detection of software supply chain attacks in code repositories,'' 2022.
\bibitem{ohm2021acme} M. Ohm et al., ``Supporting detection via unsupervised signature generation (ACME),'' 2021.
\bibitem{schorlemmer2024signing} T. R. Schorlemmer, ``Software supply chain security: Attacks, defenses, and signing adoption,'' 2024.
\bibitem{freeman1978centrality} L. C. Freeman, ``Centrality in social networks conceptual clarification,'' \textit{Social Networks}, vol. 1, no. 3, pp. 215--239, 1978.
\bibitem{watts1998smallworld} D. J. Watts and S. H. Strogatz, ``Collective dynamics of 'small-world' networks,'' \textit{Nature}, vol. 393, no. 6684, pp. 440--442, 1998.
\bibitem{newman2010networks} M. E. J. Newman, \textit{Networks: An Introduction}. Oxford University Press, 2010.
\bibitem{torres2020intoto} S. Torres-Arias, ``In-toto: Practical software supply chain security,'' in \textit{USENIX Sec.}, 2020.
\bibitem{yu2024sbom} S. Yu, ``Accurate and efficient SBOM generation for software supply chain security,'' 2024.
\bibitem{ahlstrom2025licensing} K. Ahlstrom, ``Dependency analysis for software licensing and security risk mitigation,'' 2025.

\end{thebibliography}
